Byzantine Fault-Tolerant and Locality-Aware Scheduling MapReduce

### 2019-09-12 Paper.tex
URRAAAA

Various data-intensive tasks, like seismic simulation, natural language processing, machine learning, astronomical data parsing, web data mining and many other, require a processing power that exceeds the capabilities of individual computers imposing the use of a \textit{distributed computing} \cite{LARTS}.

@@

However, as many studies confirm, \textit{hardware component failures are frequent} and they will probably happen more often in the future due to increasing number of computers connected to internet \citep{BFLMapReduce}. Is been documented that in the first year of a cluster at Google there were 1000 individual machine failures and thousands of hard drive failures \cite{PetaScaleFailure}. A recent study of DRAM errors in a large number of servers in Google data-centres for 2.5 years concluded that these errors are more prevalent than previously believed, with more than 8\% DIMM affected by errors yearly, even if protected by error correcting codes (ECC) \cite{DRAMError}. A Microsoft study of 1 million consumer PCs shown that CPU and core chipset faults are also frequent. \cite{MicrosoftStudyFailure} Moreover moving large amount of data repeatedly to distant nodes is becoming the bottleneck owing to an increased network traffic causing performance degradation.

Therefore to construct a distributed system capable to provide its services even in the presence of failures is become so critical; consequently, to provide a \textit{fault tolerant} cloud application represents an important goal in distributed-systems design.

Moreover, due to very large data-set involved during data-intensive tasks, exploiting data locality, in order to mitigate network traffic and delay, becomes very important to improve performance.

In these paper we will describe our \textit{Arbitrary Fault-Tolerant Locality-Aware} (AFTLA) MapReduce system capable to resolve all issues described above. We have implemented an AFTLA MapReduce system, capable to perform a word-count of a given text input, from scratch using Go programming language, adopting Apache ZooKeeper\textsuperscript{TM} for maintaining configuration information and system coordination \footnote{See \url{https://zookeeper.apache.org}}; all libraries used in our implementation are fully described in table \ref{tab:libraries}. Our prototype    's source code is fully available on GitHub\footnote{See \url{https://github.com/AndreaG93/SDCC-Project}}, famous web-based hosting service for version control using \texttt{git}; we remind that \LaTeX\ source code of this paper is available too\footnote{See \url{https://github.com/AndreaG93/SDCC-Project-Report}}.

@@

Our system is composed by a \textit{set of distributed processes}, every of which run on different hosts in a same data-center; in our prototype, every process run on his own Amazon EC2 server hosted in a same region (\texttt{us-east-1}). All processes interact with each other using RPC

@@

All processes are connected by \textit{reliable channels}, so no messages are lost, duplicated or corrupted; that feature is guaranteed by TCP connections. All system processes use RPC protocol in order to interact with each other.

@@

In this paper, we take for granted reader's knowledge of the MapReduce framework and Hadoop implementation. framework.

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{Architecture}
  \caption{System Architecture}
\end{figure}

Three kind of process are used in our system:

\begin{description}
\item[Client Processes] Which send word-count requests to our system sending directly an input text file.

\item[Worker Process (WP)] They execute \textit{map} or \textit{reduce} scheduled by LPP.

\item[Primary Process (PP)] It is similar to \textit{JobTracker} process used in Apache Hadoop which duty is to satisfy clients requests scheduling \textit{map} or \textit{reduce} tasks. 
\end{description}

@@

Unlike Hadoop, according to which \textit{JobTracker} process is assumed always correct, the host where PP is running may fail, for example by crashing or by losing network connectivity; in other words, as known in academic literature, PP represents a \textit{single point of failure}.

Therefore, to ensure an high system availability, adopting the same design used in Apache Mesos\textsuperscript{TM}\ \footnote{See \url{http://mesos.apache.org/documentation/latest/architecture/}}, our system architecture is based on multiple PP backup copies run on different machines; using any leader election algorithm, is possible to elect one of these copies as \textit{Leader Primary Process} (LPP) while all the others remain on stand-by. Using this approach, is possible to manage PP crash failure: when current leader fails, a backup copy is promoted to become the new leader.

LPP represents our system coordinator since only it can can interact with WP scheduling task using a \textit{push-based} approach (unlike Hadoop according to which JobTracker schedules task using a \textit{pull-based} approach \cite{LARTS})

>>>>

Various data-intensive tasks, like seismic simulation, natural language processing, machine learning, astronomical data parsing, web data mining and many others, require a processing power that exceeds the capabilities of individual computers imposing the use of a \textit{distributed computing} \cite{LARTS}.

@@

However, as many studies confirm, \textit{hardware component failures are frequent} and they will probably happen more often in the future due to increasing number of computers connected to internet \citep{BFLMapReduce}. Is been documented that in the first year of a cluster at Google there were 1000 individual machine failures and thousands of hard drive failures \cite{PetaScaleFailure}. A recent study of DRAM errors in a large number of servers in Google data-centres for 2.5 years concluded that these errors are more prevalent than previously believed, with more than 8\% DIMM affected by errors yearly, even if protected by error correcting codes (ECC) \cite{DRAMError}. A Microsoft study of 1 million consumer PCs shown that CPU and core chipset faults are also frequent \cite{MicrosoftStudyFailure}. Moreover moving large amount of data repeatedly among distant nodes is becoming the bottleneck owing to an increased network traffic, causing significant performance degradation.

Therefore to construct a distributed system capable to provide its services even in the presence of failures, that is to design a \textit{fault tolerant} cloud application, is a critical aspect of software engineering.

Moreover, due to very large data-set involved during data-intensive tasks, exploiting data locality becomes crucial aspect in order to mitigate network traffic and delay, improving so performance.

In these paper we will describe an \textit{Arbitrary Fault-Tolerant Locality-Aware} (AFTLA) MapReduce system which is capable to resolve all issues described above.

Our AFTLA MapReduce prototype, which is capable to perform a word-count by a given text input file, is been implemented from scratch using Go programming language using some external libraries, including those necessary to interact with an Apache ZooKeeper\textsuperscript{TM} cluster\footnote{\url{https://zookeeper.apache.org}}, which we have adopt for system's coordination purposes, and with Amazon AWS services, because we have adopt Amazon S3 for storage; note that all libraries used in our prototype are fully described in table \ref{tab:libraries}.

Our prototype is been design to run into several Amazon EC2 instances hosted in a same region (\texttt{us-east-1})\footnote{Note that, due to Account AWS Educate Starter limitations, we could not run Amazon EC2 instances on other regions.}, adopting AWS Elastic IP\footnote{\url{https://docs.aws.amazon.com/en_us/AWSEC2/latest/UserGuide/elastic-ip-addresses-eip.html}} to associate some of our EC2 instance to an public IPv4 address in order to enable communication with the internet and then to connect a local computer to our system.

Finally, we remember that our prototype's source code is fully available on GitHub\footnote{\url{https://github.com/AndreaG93/SDCC-Project}}, famous web-based hosting service for version control using \texttt{git}; we remind that \LaTeX\ source code of this paper is available too\footnote{See \url{https://github.com/AndreaG93/SDCC-Project-Report}}.

@@

Our system is composed by a \textit{set of distributed processes}, every of which run on different hosts in a same data-center.

@@

All processes are connected by \textit{reliable channels}, so no messages are lost, duplicated or corrupted; that feature is guaranteed by TCP connections. In our prototype, all system's processes use RPC protocol in order to interact with each other.

@@

In this paper, we take for granted reader's knowledge of the MapReduce framework and main aspects of Hadoop  framework.

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{Architecture}
  \caption{System Architecture}
  \label{fig:model}
\end{figure}

As you can see from figure \ref{fig:model}, three kind of process exist in our system:

\begin{description}
\item[Client Processes] Which sends (word-count) requests to our system.

\item[Worker Process (WP)] They execute \textit{map} or \textit{reduce} tasks scheduled by system's leader.

\item[Primary Process (PP)] It is similar to \textit{JobTracker} process used in Apache Hadoop which duty is to satisfy clients requests scheduling \textit{map} or \textit{reduce} tasks to WPs, coordinating all system. 
\end{description}

@@

Unlike Hadoop, according to which \textit{JobTracker} process is assumed always correct, we have design our system believing that the host where PP is running may fail, for example by crashing or by losing network connectivity; in other words, as known in academic literature, PP represents for us a \textit{single point of failure}.

Therefore, to ensure an high system availability, adopting the same design used in Apache Mesos\textsuperscript{TM}\ \footnote{See \url{http://mesos.apache.org/documentation/latest/architecture/}}, our system architecture is based on multiple PP backup copies run on \textit{different machines} (in our prototype, on different EC2 instances); using a leader election algorithm, is possible to elect one of these copies as leader, becoming the \textit{Leader Primary Process} (LPP), while all the others remain on stand-by. Using this approach, is possible to manage PP crash failure: when current LPP fails, a backup copy is promoted to become the new leader.

, only LPP can interact with WPs and modify data into the Zookeeper Cluster. Note that LPP schedules several task using a \textit{push-based} approach (unlike Hadoop according to which JobTracker schedules task using a \textit{pull-based} approach \cite{LARTS})
